---
title: "Untitled"
format: html
editor: visual
---

## 

## 15.6 Practice

```{r}
library(babynames) 
library(tidyverse)
```

Hello guys, so far we learn some useful functions. So let's do some practice !

In the first example I want to select all sentences start with ''The'' article. We can do that with \^ anchor.

Our code is

```{r}
str_view(sentences,"^The")
```

we can see that the pattern also match another sentectes like 'These'. To fix this problem we need to ensure that the letter 'e' is the last letter in the word."

If we add boundary to the pattern it will work.

So, our code like this:

```{r}
str_view(sentences,"^The\\b")
```

All sentences start with 'The' article.

Also we can write this code add boundary to both sides of the pattern.

So, our code like this:

```{r}
str_view(sentences,"\\bThe\\b")
```

But we couldn't do this if our sentences data were all lowercase letters.

I can give you a simple example

This is our example data

```{r}
example <- c("statistics are the best","the mean of sample is a statistic")
```

```{r}
str_view(example,"\\bthe\\b")
```

Again ı want sentences start with 'the' article but this time code select correct one and also select wrong one. Boundary does not make any limitation like anchor.

So, what can we do if we want to select all sentences begin with a pronoun

Our code like this:

```{r}
str_view(sentences,"^She|He|It|They\\b")
```

Similar to first example our code match another sentences like 'Help'. If we add parantheses we can fix the problem. It is similar to multiplication in math.

```{r}
str_view(sentences,"^(She|He|It|They)\\b")
```

We can notice the mistakes we made because we see them in the first parts of the data.If this does not happen, we can check our code by creating a test set.

```{r}
pos <- c("He is a boy","She had a good time") 
neg <- c("Shells come from the sea","Headley said 'It's a great day'") 
pattern <- "^(She|He|It|They)\\b"
```

```{r}
str_detect(pos,pattern)  
```

In the first code we expect TRUE value.

```{r}
str_detect(neg,pattern)
```

And the second one we expect FALSE value

Also You use this code to check

```{r}
str_view(pos,pattern)
```

```{r}
str_view(neg,pattern)
```

so our pattern works as expected!
